### 2009-04-13 docs/runtime_parameters/runtime_parameters.tex
more progress

                                      predict\_Tprime\_then\_h = 6;  &  predict\_rhohprime \\

@@

\verb=  temp_diffusion_formulation =  &   &  .false. \\
\verb=  test_set =  &   &  '' \\
\verb=  the_copy_cache_max =  &   & 50 \\
\verb=  the_knapsack_verbosity =  &   &  .false. \\

@@

\verb=  thermal_diffusion_type =  &   &  1 \\
\verb=  the_sfc_threshold =  &   & 5 \\

@@

\verb=  use_divu_firstdt =  &   &  .false. \\

@@

\verb=  use_soundspeed_firstdt =  &   &  .false. \\
\verb=  use_tfromp =  &   &  .false. \\
\verb=  use_thermal_diffusion =  &   &  .false. \\
\verb=  velpert_amplitude =  &   &  0.d0 \\
\verb=  velpert_radius =  &   &  0.75d8 \\
\verb=  velpert_scale =  &   &  0.8d8 \\
\verb=  velpert_steep =  &   &  1.d0 \\
\verb=  verbose =  &   &  0 \\
\verb=  w0mac_interp_type =  &   &  1 \\
\verb=  xrb_pert_factor =  &   &  1.d-2 \\
\verb=  xrb_pert_size =  &   &  5.0d1 \\
\verb=  xrb_pert_type =  &   &  1 \\
\verb=  xrb_use_bottom_sponge =  &   &  .true. \\

>>>>

                                      predict\_Tprime\_then\_h = 6.  &  predict\_rhohprime \\

@@

\verb=  temp_diffusion_formulation =  & How to compute the explicit thermal diffusion
                                                term.  .true. = in terms of $T$; .false. =
                                                in terms of $\rho,p_0,X$.  &  .false. \\
\verb=  test_set =  & Fixed grid file.  &  '' \\
\verb=  the_copy_cache_max =  & Number of boxassoc layouts we keep in memory to avoid 
                                      having to recompute the boxassoc, which is 
                                      computationally expensive.  & 50 \\
\verb=  the_knapsack_verbosity =  & Verbosity of the knapscak processor-to-grid
                                           algorithm.  &  .false. \\

@@

\verb=  thermal_diffusion_type =  & In the thermal diffusion solver, 1 = 
                                           Crank-Nicholson; 2 = Backward Euler.  &  1 \\
\verb=  the_sfc_threshold =  & When assigning processors for grids, this determines 
                                     whether we use the sfc algorithm or knapsack 
                                     algorithm.  If the total number of grids divided by 
                                     the number of processors is greater than this number, 
                                     use sfc.  & 5 \\

@@

\verb=  use_divu_firstdt =  & Use the divu constraint when computing the first
                                   time step.  &  .false. \\

@@

\verb=  use_soundspeed_firstdt =  & Use the soundspeed constraint when computing the
                                           first time step.  &  .false. \\
\verb=  use_tfromp =  & When updating temperature, use $T=T(\rho,p_0,X) $ rather than
                            $T=T(\rho,h,X)$. &  .false. \\
\verb=  use_thermal_diffusion =  & Use thermal diffusion.  &  .false. \\
\verb=  velpert_amplitude =  & (spherical stars only) Amplitude of random Fourier
                                     modes.  &  0.d0 \\
\verb=  velpert_radius =  & (spherical stars only) Cutoff radius where we start 
                                 applying a tanh function to decay the random Fourier
                                 modes. &  0.75d8 \\
\verb=  velpert_scale =  & (spherical stars only) Square length which defines the 
                                random Fourier modes correspond to. &  0.8d8 \\
\verb=  velpert_steep =  & (spherical stars only) Steepness of the cutoff of the random
                                Fourier modes. &  1.d0 \\
\verb=  verbose =  & General verbosity  &  0 \\
\verb=  w0mac_interp_type =  & 0 = Compute w0 at edges using a projection; 1 = 
                                     Interpolate w0 to cell centers, then average to edges; 
                                     2 = Interpolate w0 to edges directly; 3 = Interpolate 
                                     w0 to nodes, then average to edges.  &  1 \\
\verb=  xrb_pert_factor =  & (xrb problem only) Increase in amplitude of 
                                  perturbational quantity relative to ambient. &  1.d-2 \\
\verb=  xrb_pert_size =  & (xrb problem only)  Width of Gaussian distribution &  5.0d1 \\
\verb=  xrb_pert_type =  & (xrb problem only) 1 = perturb temperature; 2 = perturb 
                                density. &  1 \\
\verb=  xrb_use_bottom_sponge =  & (xrb problem only)  Put a sponge at the bottom of 
                                          the domain.  &  .true. \\
